\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Alen Sarang Satheesh - Resume},
}

\titleformat{\section}{\Large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\begin{document}

\begin{center}
    {\huge \textbf{Alen Sarang Satheesh}} \\ \vspace{4pt}
    Freelance Software Engineer \& Automation Expert \\ \vspace{4pt}
    \href{mailto:alensarangsatheesh@gmail.com}{alensarangsatheesh@gmail.com} $|$ 
    +91-8075896213 $|$ 
    \href{https://linkedin.com/in/alen-sarang-satheesh}{linkedin.com/in/alen-sarang-satheesh} $|$ 
    \href{https://alensarangsatheesh.github.io}{alensarangsatheesh.github.io}
\end{center}

\vspace{10pt}

\section{Summary}
Experienced Freelance Software Engineer specializing in full-stack web applications, Chrome extensions, reverse engineering, and business automation. Demonstrated expertise in creating dynamic single-page applications (SPAs), CRMs, and complex plugins. Additionally skilled in cyber security, offering expert penetration testing and vulnerability assessments. Proven ability to deliver comprehensive technical solutions from architecture to secure deployment.

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Software Development:} Full-stack SPAs, dynamic websites, custom CRMs, API integration
    \item \textbf{Tools \& Automation:} Chrome extensions, agentic software, LLM integration, desktop automation scripts, OCR
    \item \textbf{Cyber Security:} Penetration testing, vulnerability assessments, Burp Suite enhancement
    \item \textbf{Reverse Engineering:} Desktop plugins (e.g., AutoCAD), protocol analysis
\end{itemize}

\section{Experience \& Services}
\textbf{Freelance Software Engineer \& Security Analyst} \hfill \textit{Current} \\
\textit{International \& National Clients}
\begin{itemize}[leftmargin=0.25in]
    \item \textbf{Web Apps \& CRMs:} Architected and developed full-stack dynamic SPAs, custom CRMs, and complex business software. Delivered highly customized software solutions optimizing client workflows.
    \item \textbf{Extensions \& Reverse Engineering:} Built highly-rated Chrome extensions (5-stars, 90+ active users) like bridging Chartink to TradingView. Reverse-engineered complex desktop plugins achieving up to 90\% feature parity with original software like AutoCAD's AutoRebar.
    \item \textbf{Agentic AI \& Automation:} Developed cutting-edge agentic AI-driven tools to automate repetitive business tasks. Created scalable automation scripts across varying platforms including WhatsApp and Instagram.
    \item \textbf{Security Auditing:} Conducted comprehensive penetration tests for platforms (e.g., FreeSewing), identifying and reporting critical backend vulnerabilities.
\end{itemize}

\section{Featured Projects}
\textbf{AutoCAD AutoRebar Clone} \hfill \textit{Reverse Engineering}
\begin{itemize}[leftmargin=0.25in]
    \item Reverse-engineered and recreated a complex desktop plugin from scratch achieving 90\% feature parity to the original AutoRebar tool for AutoCAD.
\end{itemize}

\textbf{Chartink to TradingView/Screener Extension} \hfill \textit{Browser Extension}
\begin{itemize}[leftmargin=0.25in]
    \item Developed a 5-star rated Chrome extension bridging Chartink screeners and TradingView charts for a seamless trading workflow. Active user base of 90+ users.
\end{itemize}

\textbf{FreeSewing Penetration Test} \hfill \textit{Cyber Security}
\begin{itemize}[leftmargin=0.25in]
    \item Executed comprehensive security assessment identifying critical backend vulnerabilities. Findings were officially disclosed and patched.
\end{itemize}

\textbf{Tent-Camp-Website} \hfill \textit{Web Application}
\begin{itemize}[leftmargin=0.25in]
    \item Built a full-stack, responsive web application enabling users to browse and reserve tent camping experiences.
\end{itemize}

\textbf{Automation Scripts \& Tools} \hfill \textit{Automation \& AI}
\begin{itemize}[leftmargin=0.25in]
    \item \textbf{WhatsApp Bulk Sender \& Instagram Auto-Reply Bot:} Created simulation-based interaction tools for efficient, automated social media engagement.
    \item \textbf{Burp-Enhanced-Logger:} Developed an enhanced logging tool for Burp Suite to streamline penetration testing workflows and data analysis.
    \item \textbf{Screenshot Phone Number Extractor:} Built an OCR-based utility to rapidly extract phone numbers directly from image screenshots.
\end{itemize}
\end{document}
